Supplementary Information: \nTree height, microhabitat, and hydraulic traits shape drought responses in a temperate broadleaf forest

### 2020-07-21 manuscript/climate_sensitivity_SI.Rmd
update R2, Tables S6/S7
#119 , #98

\newpage
```{r table S6, eval = TRUE, echo=FALSE, warning=FALSE}
library(knitr)
library(kableExtra)
multivar_table <- read.csv("tables_figures/publication/table5_multivariable_models_lmer_CPout.csv", stringsAsFactors = FALSE, check.names = FALSE) 
kable(multivar_table, booktabs = TRUE, caption = "Table S6. Summary of top full models for each drought instance, where $Rt$ is used as the response variable. ", format = 'latex', escape = FALSE) %>%
  kable_styling(latex_options = c("scale_down", "hold_position"), font_size = 12, protect_latex = TRUE) %>%
  pack_rows("", 1, 4, latex_gap_space = ".4em", colnum = 1, hline_before = FALSE) %>%
  pack_rows("", 5, 5, latex_gap_space = ".4em", colnum = 1, hline_before = FALSE) %>%
  pack_rows("", 6, 10, latex_gap_space = ".4em", colnum = 1, hline_before = FALSE) %>%
  pack_rows("", 11, 16, latex_gap_space = ".4em", colnum = 1, hline_before = FALSE) %>%
  row_spec(1, bold = T) %>%
  row_spec(5, bold = T) %>%
  row_spec(6, bold = T) %>%
  row_spec(11, bold = T) %>%
  kable_styling()
```
Models are ranked by AICc. Shown are all models whose AICc value falls within 2.0 ($\Delta$AICc<1) of the best model (bold).

\newpage
```{r table S7, eval = TRUE, echo=FALSE, warning=FALSE}
library(knitr)
library(kableExtra)
multivar_table <- read.csv("tables_figures/publication/tableS6_multivariable_models_lmer_arimaratio_CPout.csv", stringsAsFactors = FALSE, check.names = FALSE) 
kable(multivar_table, booktabs = TRUE, caption = "Table S7. Summary of top  models for each drought instance, where $Rt_{ARIMA}$ is used as the response variable. ", format = 'latex', escape = FALSE) %>%
  kable_styling(latex_options = c("scale_down", "hold_position"), font_size = 12, protect_latex = TRUE) %>%
  pack_rows("", 1, 4, latex_gap_space = ".4em", colnum = 1, hline_before = FALSE) %>%
  pack_rows("", 5, 7, latex_gap_space = ".4em", colnum = 1, hline_before = FALSE) %>%
  pack_rows("", 8, 14, latex_gap_space = ".4em", colnum = 1, hline_before = FALSE) %>%
  pack_rows("", 15, 25, latex_gap_space = ".4em", colnum = 1, hline_before = FALSE) %>%
  row_spec(1, bold = T) %>%
  row_spec(5, bold = T) %>%
  row_spec(8, bold = T) %>%
  row_spec(15, bold = T) %>%
  kable_styling()
```
Models are ranked by AICc. Shown are all models whose AICc value falls within 2.0 ($\Delta$AICc<1) of the best model (bold).

>>>>

\newpage
```{r table S6, eval = TRUE, echo=FALSE, warning=FALSE}
library(knitr)
library(kableExtra)
multivar_table <- read.csv("tables_figures/publication/tableS6_multivariable_models_lmer_CPout.csv", stringsAsFactors = FALSE, check.names = FALSE) 
kable(multivar_table, booktabs = TRUE, caption = "Table S6. Summary of top full models for each drought instance, where $Rt$ is used as the response variable. ", format = 'latex', escape = FALSE) %>%
  kable_styling(latex_options = c("scale_down", "hold_position"), font_size = 12, protect_latex = TRUE) %>%
  pack_rows("", 1, 4, latex_gap_space = ".4em", colnum = 1, hline_before = FALSE) %>%
  pack_rows("", 5, 5, latex_gap_space = ".4em", colnum = 1, hline_before = FALSE) %>%
  pack_rows("", 6, 10, latex_gap_space = ".4em", colnum = 1, hline_before = FALSE) %>%
  pack_rows("", 11, 16, latex_gap_space = ".4em", colnum = 1, hline_before = FALSE) %>%
  row_spec(1, bold = T) %>%
  row_spec(5, bold = T) %>%
  row_spec(6, bold = T) %>%
  row_spec(11, bold = T) %>%
  kable_styling()
```
Models are ranked by AICc. Shown are all models whose AICc value falls within 2.0 ($\Delta$AICc<1) of the best model (bold). $R^2$ refers to conditional $R^2$.

\newpage
```{r table S7, eval = TRUE, echo=FALSE, warning=FALSE}
library(knitr)
library(kableExtra)
multivar_table <- read.csv("tables_figures/publication/tableS7_multivariable_models_lmer_arimaratio_CPout.csv", stringsAsFactors = FALSE, check.names = FALSE) 
kable(multivar_table, booktabs = TRUE, caption = "Table S7. Summary of top  models for each drought instance, where $Rt_{ARIMA}$ is used as the response variable. ", format = 'latex', escape = FALSE) %>%
  kable_styling(latex_options = c("scale_down", "hold_position"), font_size = 12, protect_latex = TRUE) %>%
  pack_rows("", 1, 4, latex_gap_space = ".4em", colnum = 1, hline_before = FALSE) %>%
  pack_rows("", 5, 7, latex_gap_space = ".4em", colnum = 1, hline_before = FALSE) %>%
  pack_rows("", 8, 14, latex_gap_space = ".4em", colnum = 1, hline_before = FALSE) %>%
  pack_rows("", 15, 25, latex_gap_space = ".4em", colnum = 1, hline_before = FALSE) %>%
  row_spec(1, bold = T) %>%
  row_spec(5, bold = T) %>%
  row_spec(8, bold = T) %>%
  row_spec(15, bold = T) %>%
  kable_styling()
```
Models are ranked by AICc. Shown are all models whose AICc value falls within 2.0 ($\Delta$AICc<1) of the best model (bold). $R^2$ refers to conditional $R^2$.
